Concentration Inequalities

### 2015-10-22 causal-bandit/observe_then_best.tex
prep for tpr talk

\begin{enumerate}
\item The learner chooses an $I_t \in \set{1,\ldots, N}$ and $J_t \in \set{0,1}$.
\item Then $X_t \in \set{0,1}^N$ is sampled from a product of Bernoulli distributions, $X_{t,i} \sim \Ber(q_i)$ 
\item The learner observes $\tilde X_t \in \set{0,1}^K$, which is defined by 
\eq{
\tilde X_{t,i} = \begin{cases}
X_{t,i} &\text{if } i \neq I_t \\
J_t & \text{otherwise}\,.
\end{cases}
}
\item The learner receives reward $Y_t \sim \Ber(r(\tilde X))$ where $r:\set{0,1}^K \to [0,1]$ is unknown and arbitrary.
\end{enumerate}

@@

We now have an additional trade off to make, which is how much should be observe (learning something about at least half the arms each timestep) versus playing the low probability arms.

>>>>

\begin{enumerate}
\item The learner chooses an $I_t \in \set{1,\ldots, N}$ and $J_t \in \set{0,1}$.
\item Then $X_t \in \set{0,1}^N$ is sampled from a product of Bernoulli distributions, $X_{t,i} \sim \Ber(q_i)$ 
\item The learner observes $\tilde X_t \in \set{0,1}^K$, which is defined by 
\eq{
\tilde X_{t,i} = \begin{cases}
X_{t,i} &\text{if } i \neq I_t \\
J_t & \text{otherwise}\,.
\end{cases}
}
\item The learner receives reward $Y_t \sim \Ber(r(\tilde X))$ where $r:\set{0,1}^K \to [0,1]$ is unknown and arbitrary. THIS LOOKS WRONG SHOULD BE N not K.
\end{enumerate}

@@

We now have an additional trade off to make, which is how much should be observe (learning something about half the arms each timestep) versus playing the low probability arms.
